Supplementary Information

### 2021-02-08 doc/manuscript/MEE_manuscript.Rmd
add author affiliations

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander^5^,
Craig D. Allen,
Raquel Alfaro-Sánchez^wl^,
Tala Awada,
Jennifer L. Baltzer^wl^,
Patrick J. Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart J. Davies^2^,
Cameron Dow^1^,
Ryan Helcoski^1^,
[Jakub Kašpar^cz^](0000-0003-1780-6310),
James Lutz,
Ellis Q. Margolis,
Justin Maxwell^jm^,
Sean McMahon^2^,
Camille Piponiot^1,2^,
Sabrina Russo,
[Pavel Šamonil^cz^](0000-0002-7722-8797),
Anastasia Sniderhan^wl^,
Alan J. Tepley^1,at^,
[Ivana Vašíčková^cz^](0000-0002-6070-5956), 
Mart Vlam,
Peter Zuidema

@@

wl. Biology Department, Wilfrid Laurier University, 75 University Ave W, Waterloo, ON, N2L 3C5

at. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

cz. Department of Forest Ecology, The Silva Tarouca Research Institute for Landscape and Ornamental Gardening, Lidická 25/27, 602 00 Brno, Czech Republic

jm. Department of Geography, Indiana University, Bloomington, Indiana, USA

>>>>

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander^5^,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
Sarayudh Bunyavejchewin^10^,
Paolo Cherubini^11^,
Justin Cooper^12^,
Stuart J. Davies^2^,
Cameron Dow^1,13^,
Ryan Helcoski^1^,
[Jakub Kašpar](0000-0003-1780-6310)^14^,
[James Lutz]( 0000-0002-2560-0710)^12^,
Ellis Q. Margolis^6^,
Justin Maxwell^15^,
Sean McMahon^2,16^,
Camille Piponiot^1,2, 17^,
Sabrina Russo^8^,
[Pavel Šamonil](0000-0002-7722-8797)^14^,
Anastasia Sniderhan^7^,
Alan J. Tepley^1,18^,
[Ivana Vašíčková](0000-0002-6070-5956)^14^, 
Mart Vlam^19^,
Peter Zuidema^19^

@@

6. U.S. Geological Survey, Fort Collins Science Center, Jemez Mountains Field Station, Los Alamos, NM 87544, USA

7. Biology Department, Wilfrid Laurier University, 75 University Ave W, Waterloo, ON, N2L 3C5

8. School of Natural Resources, University of Nebraska-Lincoln, Lincoln, NE 68583, USA

9. School of Biological Sciences, Monash University, Clayton, Victoria 3800, Australia

10. National Parks Wildlife and Plant Conservation Department, Chatuchak, Bangkok 10900, Thailand

11. Swiss Federal Institute for Forest, Snow and Landscape Research, CH-8903 Birmensdorf, Switzerland

12. S. J. & Jessie E. Quinney College of Natural Resources and the Ecology Center, Utah State University, Logan, UT 84322, USA

13. Department of Forestry, Purdue University, West Lafayette, IN 47907, USA

14. Department of Forest Ecology, The Silva Tarouca Research Institute for Landscape and Ornamental Gardening, Lidická 25/27, 602 00 Brno, Czech Republic

15. Department of Geography, Indiana University, Bloomington, Indiana, USA

16. Smithsonian Environmental Research Center, Edgewater, MD, USA

17. CIRAD, Montpellier, France

18. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

19. Forest Ecology and Forest Management Group, Wageningen; Wageningen, The Netherlands
